% arara: pdflatex: {synctex: yes, interaction: nonstopmode}
% arara: pdflatex: {synctex: yes, interaction: nonstopmode} until !( found('log', 'LaTeX Warning: Citation') || found('log', 'LaTeX Warning: Label') || found('log', 'LaTeX Warning: Reference') || found('log', 'There were undefined references') )

% if `LaTeX Warning: Citation' found in log, run `arara root.tex` again

%%%
 % File: /latex/big-cocluster-paper/root.tex
 % Created Date: Thursday, July 11th 2024
 % Author: Zihan
 % -----
 % Last Modified: Monday, 5th August 2024 10:56:08 pm
 % Modified By: the developer formerly known as Zihan at <wzh4464@gmail.com>
 % -----
 % HISTORY:
 % Date      		By   	Comments
 % ----------		------	---------------------------------------------------------
%%%

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command
\overrideIEEEmargins                                      % Needed to meet printer requirements.

% \usepackage{arxiv}
\usepackage{algorithm,algorithmic}
\usepackage{bm}
\usepackage{amsmath}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{lipsum}         % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{multirow}       % multirow in table
% \usepackage[numeric]{natbib}
% \usepackage[backend=biber,style=ieee]{biblatex}
% \bibliography{references}  
% \DeclareFieldFormat{url}{}
% \DeclareFieldFormat{urldate}{}
\usepackage{doi}
\usepackage{threeparttable}
\usepackage{xcolor}
\usepackage{subcaption}

 
% theorems
% \usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

% Cref for lemma
\crefname{lemma}{lemma}{lemmas}
\Crefname{lemma}{Lemma}{Lemmas}
\crefname{assumption}{assumption}{assumptions}
\Crefname{assumption}{Assumption}{Assumptions}
\crefname{definition}{definition}{definitions}
\Crefname{definition}{Definition}{Definitions}

% set import path of input files
\makeatletter
\def\input@path{{sections/}}
\makeatother

% set image path
\graphicspath{{images/}}

\title{\LARGE \bf Scalable Co-Clustering for Large-Scale Data through Dynamic Partitioning and Hierarchical Merging}

\author{Zihan Wu$^{1}$, Zhaoke Huang$^{2}$, and Hong Yan$^{3}$% <-this % stops a space
\thanks{This work is supported by Hong Kong Innovation and
Technology Commission (InnoHK Project CIMDA) and Hong
Kong Research Grants Council (Project CityU 11204821).}% <-this % stops a space
\thanks{$^{1}$Zihan Wu (Corresponding Author) is with the Department of Electrical Engineering,
        City University of Hong Kong, Hong Kong
        {\tt\small zihan.wu@my.cityu.edu.hk}}%
\thanks{$^{2}$Zhaoke Huang is with the Department of Electrical Engineering,
        City University of Hong Kong, Hong Kong
        {\tt\small Z.Huang@cityu.edu.hk}}%
\thanks{$^{3}$Hong Yan is with the Department of Electrical Engineering,
        City University of Hong Kong, Hong Kong
        {\tt\small h.yan@cityu.edu.hk}}%
}
\hypersetup{
pdftitle={Scalable Co-Clustering for Large-Scale Data through Dynamic Partitioning and Hierarchical Merging},
pdfsubject={Artificial Intelligence, Machine Learning, Data Mining},
pdfauthor={Zihan Wu, Zhaoke Huang, Hong Yan},
pdfkeywords={Co-clustering, Large-scale data, Matrix partitioning, Hierarchical merging},
}

\begin{document}
\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\input{abstract.tex}
\input{introduction.tex}
\input{related_work.tex}
\input{method.tex}
\input{experiment.tex}
\input{conclusion.tex}
% \input{appendix.tex}

% \section*{Acknowledgment}
% This work is supported by Hong Kong Innovation and Technology
% Commission (InnoHK Project CIMDA) and Hong Kong Research Grants
% Council (Project CityU 11204821).

% \begin{table}[b]
% 	\caption{Sample table title}
% 	\centering
% 	\begin{tabular}{lll}
% 		\toprule
% 		\multicolumn{2}{c}{Part}                   \\
% 		\cmidrule(r){1-2}
% 		Name     & Description     & Size ($\mu$m) \\
% 		\midrule
% 		Dendrite & Input terminal  & $\sim$100     \\
% 		Axon     & Output terminal & $\sim$10      \\
% 		Soma     & Cell body       & up to $10^6$  \\
% 		\bottomrule
% 	\end{tabular}
% 	\label{tab:table}
% \end{table}

% Generated by IEEEtran.bst, version: 1.14 (2015/08/26)
\begin{thebibliography}{10}
        \providecommand{\url}[1]{#1}
        \csname url@samestyle\endcsname
        \providecommand{\newblock}{\relax}
        \providecommand{\bibinfo}[2]{#2}
        \providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
        \providecommand{\BIBentryALTinterwordstretchfactor}{4}
        \providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
                \BIBentryALTinterwordstretchfactor\fontdimen3\font minus
                \fontdimen4\font\relax}
        \providecommand{\BIBforeignlanguage}[2]{{%
                                \expandafter\ifx\csname l@#1\endcsname\relax
                                        \typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
                                        \typeout{** loaded for the language `#1'. Using the pattern for}%
                                        \typeout{** the default language instead.}%
                                \else
                                        \language=\csname l@#1\endcsname
                                \fi
                                #2}}
        \providecommand{\BIBdecl}{\relax}
        \BIBdecl

        \bibitem{zhang2023AdaptiveGraphConvolution}
        X.~Zhang, H.~Liu, Q.~Li, X.-M. Wu, and X.~Zhang, ``Adaptive graph convolution
        methods for attributed graph clustering,'' \emph{IEEE Transactions on
                Knowledge and Data Engineering}, vol.~35, no.~12, pp. 12\,384--12\,399, 2023.

        \bibitem{wu2023EffectiveClusteringStructured}
        D.~Wu, F.~Nie, J.~Lu, R.~Wang, and X.~Li, ``Effective clustering via structured
        graph learning,'' \emph{IEEE Transactions on Knowledge and Data Engineering},
        vol.~35, no.~8, pp. 7909--7920, 2023.

        \bibitem{chen2023FastFlexibleBipartite}
        W.~Chen, H.~Wang, Z.~Long, and T.~Li, ``Fast flexible bipartite graph model for
        co-clustering,'' \emph{IEEE Transactions on Knowledge and Data Engineering},
        vol.~35, no.~7, pp. 6930--6940, 2023.

        \bibitem{zhao2023MultiviewCoclusteringMultisimilarity}
        L.~Zhao, Y.~Ma, S.~Chen, and J.~Zhou, ``Multi-view co-clustering with
        multi-similarity,'' \emph{Applied Intelligence}, vol.~53, no.~13, pp.
        16\,961--16\,972, 2023.

        \bibitem{kumar2023CoclusteringBasedMethods}
        N.~Kumar and M.~Sheeba, ``Co-clustering based methods and their significance
        for recommender systems,'' in \emph{Multi-Disciplinary Trends in Artificial
                Intelligence: 16th International Conference, MIWAI 2023, Hyderabad, India,
                July 21-22, 2023, Proceedings}, vol. 14078, 2023, pp. 513--522.

        \bibitem{kluger2003SpectralBiclusteringMicroarray}
        Y.~Kluger, R.~Basri, J.~T. Chang, and M.~Gerstein, ``Spectral biclustering of
        microarray data: Coclustering genes and conditions,'' \emph{Genome Research},
        vol.~13, no.~4, pp. 703--716, 2003.

        \bibitem{yan2017CoclusteringMultidimensionalBig}
        H.~Yan, ``Coclustering of multidimensional big data: A useful tool for genomic,
        financial, and other data analysis,'' \emph{IEEE Systems, Man, and
                Cybernetics Magazine}, vol.~3, no.~2, pp. 23--30, 2017.

        \bibitem{higham2007SpectralClusteringIts}
        D.~J. Higham, G.~Kalna, and M.~Kibble, ``Spectral clustering and its use in
        bioinformatics,'' \emph{Journal of Computational and Applied Mathematics},
        vol. 204, no.~1, pp. 25--37, 2007.

        \bibitem{zhao2012BiclusteringAnalysisPattern}
        H.~Zhao, A.~Wee-Chung~Liew, D.~Z.~Wang, and H.~Yan, ``Biclustering analysis for
        pattern discovery: Current techniques, comparative studies and
        applications,'' \emph{Current Bioinformatics}, vol.~7, no.~1, pp. 43--55,
        2012.

        \bibitem{dhillon2007WeightedGraphCuts}
        I.~S. Dhillon, Y.~Guan, and B.~Kulis, ``Weighted graph cuts without
        eigenvectors a multilevel approach,'' \emph{IEEE Transactions on Pattern
                Analysis and Machine Intelligence}, vol.~29, no.~11, pp. 1944--1957, 2007.

        \bibitem{chen2023ParallelNonNegativeMatrix}
        Y.~Chen, Z.~Lei, Y.~Rao, H.~Xie, F.~L. Wang, J.~Yin, and Q.~Li, ``Parallel
        non-negative matrix tri-factorization for text data co-clustering,''
        \emph{IEEE Transactions on Knowledge and Data Engineering}, vol.~35, no.~5,
        pp. 5132--5146, 2023.

        \bibitem{hansen2011NonparametricCoclusteringLarge}
        T.~J. Hansen, M.~Morup, and L.~Kai~Hansen,
        ``\BIBforeignlanguage{en}{Non-parametric co-clustering of large scale sparse
                bipartite networks on the {GPU}},'' in \emph{\BIBforeignlanguage{en}{2011
                                {IEEE} {International} {Workshop} on {Machine} {Learning} for {Signal}
                                {Processing}}}, Beijing, China, Sep. 2011, pp. 1--6.

        \bibitem{pan2008CRDFastCoclustering}
        F.~Pan, X.~Zhang, and W.~Wang, ``\BIBforeignlanguage{en}{{CRD}: fast
                co-clustering on large datasets utilizing sampling-based matrix
                decomposition},'' in \emph{\BIBforeignlanguage{en}{Proceedings of the 2008
                                {ACM} {SIGMOD} {International} {Conference} on {Management} of {Data}}}, vol.
        2008.\hskip 1em plus 0.5em minus 0.4em\relax Vancouver Canada: ACM, Jun.
        2008, pp. 173--184.

        \bibitem{long2005CoclusteringBlockValue}
        B.~Long, Z.~Zhang, and P.~S. Yu, ``\BIBforeignlanguage{en}{Co-clustering by
                block value decomposition},'' in \emph{\BIBforeignlanguage{en}{Proceedings of
                        the eleventh {ACM} {SIGKDD} {International} {Conference} on {Knowledge}
                                {Discovery} in {Data} {Mining}}}, ser. {KDD} '05.\hskip 1em plus 0.5em minus
        0.4em\relax New York, NY, USA: Association for Computing Machinery, 2005, pp.
        635--640.

        \bibitem{dongkuanxu2019DeepCoClustering}
        D.~Xu, W.~Cheng, B.~Zong, J.~Ni, D.~Song, W.~Yu, Y.~Chen, H.~Chen, and
        X.~Zhang, ``Deep co-clustering,'' in \emph{Proceedings of the 2019 SIAM
                International Conference on Data Mining}, 2019, pp. 414--422.

        \bibitem{cheng2015CoClusterDDistributedFramework}
        X.~Cheng, S.~Su, L.~Gao, and J.~Yin, ``Co-{{ClusterD}}: {{A}} distributed
        framework for data co-clustering with sequential updates,'' \emph{IEEE
                Transactions on Knowledge and Data Engineering}, vol.~27, no.~12, pp.
        3231--3244, 2015.

        \bibitem{vonluxburg2007TutorialSpectralClustering}
        U.~von Luxburg, ``A tutorial on spectral clustering,'' \emph{Statistics and
                Computing}, vol.~17, no.~4, pp. 395--416, 2007.

        \bibitem{dhillon2001CoclusteringDocumentsWords}
        I.~S. Dhillon, ``Co-clustering documents and words using bipartite spectral
        graph partitioning,'' in \emph{Knowledge Discovery and Data Mining}, 2001.

        \bibitem{ni2019justifying}
        J.~Ni, J.~Li, and J.~McAuley, ``\BIBforeignlanguage{en}{Justifying
                recommendations using distantly-labeled reviews and fine-grained aspects},''
        in \emph{\BIBforeignlanguage{en}{Proceedings of the 2019 {Conference} on
                {Empirical} {Methods} in {Natural} {Language} {Processing} and the 9th
                {International} {Joint} {Conference} on {Natural} {Language} {Processing}
        ({EMNLP}-{IJCNLP})}}.\hskip 1em plus 0.5em minus 0.4em\relax Hong Kong,
        China: Association for Computational Linguistics, 2019, pp. 188--197.

        \bibitem{reddy2021weclustering}
        G.~S. Reddy, P.~K. Reddy, and A.~R. Reddy, ``Weclustering: Word embeddings
        based text clustering technique for high dimensional data,'' \emph{Applied
                Intelligence}, vol.~51, no.~5, pp. 2376--2394, 2021.

        \bibitem{lewis2004rcv1}
        D.~D. Lewis, Y.~Yang, T.~G. Rose, and F.~Li, ``Rcv1: A new benchmark collection
        for text categorization research,'' \emph{Journal of Machine Learning
                Research}, vol.~5, pp. 361--397, 2004.

\end{thebibliography}


% \input{appendix.tex}

\end{document}
